---
title: "Homework 2"
author: "Seungjoon Yoo"
date: "2/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
# Imports the US Airports Data

 data("USairports", package = "igraphdata")
  network_igraph <- USairports
  rm(USairports)
```

```{r}
  if("statnet" %in% rownames(installed.packages()) == FALSE) {install.packages("statnet")}
  if("igraph"  %in% rownames(installed.packages()) == FALSE) {install.packages("igraph")}
  if("igraphdata" %in% rownames(installed.packages()) == FALSE) {install.packages("igraphdata")}

  library(statnet)
  library(igraph)
  library(igraphdata)
```

```{r}
#Now let's make an edgelist versian

    network_edgelist <- as.data.frame(as_edgelist(network_igraph), stringsAsFactors = FALSE)
  
  #Lets add edge attributes
    network_edgelist$Carrier    <- as.character(E(network_igraph)$Carrier)
    network_edgelist$Departures <- as.character(E(network_igraph)$Departures)
    network_edgelist$Seats      <- as.character(E(network_igraph)$Seats)
    network_edgelist$Passengers <- as.character(E(network_igraph)$Passengers)
    network_edgelist$Aircraft   <- as.character(E(network_igraph)$Aircraft)
    network_edgelist$Distance   <- as.character(E(network_igraph)$Distance)
    network_edgelist$weight <- as.character(E(network_igraph)$Passengers)
```

```{r}    
#Now let's create a node attribute dataframe
    network_nodes <- data.frame(name = as.character(V(network_igraph)$name), 
                                City = as.character(V(network_igraph)$City),
                                Position = as.character(V(network_igraph)$Position),
                                stringsAsFactors = FALSE)
```

```{r}
#Lets create an statnet network object from our edgelist
  network_statnet <- network(as.matrix(network_edgelist[1:2]), matrix.type = 'edgelist', directed = TRUE)
  
  network_statnet%e%'Carrier'    <- network_edgelist$Carrier    
  network_statnet%e%'Departures' <- network_edgelist$Departures 
  network_statnet%e%'Seats'      <- network_edgelist$Seats      
  network_statnet%e%'Passangers' <- network_edgelist$Passengers 
  network_statnet%e%'Aircraft'   <- network_edgelist$Aircraft   
  network_statnet%e%'Distance'   <- network_edgelist$Distance
  network_statnet%e%'weight' <- network_edgelist$Passengers 
  
  
  network_statnet%v%'City'       <- as.character(network_nodes$City)
  network_statnet%v%'Distance'   <- as.character(network_nodes$Distance)
```  

```{r}  
#Let's add a helpful message that will tell  users what this script has done.
  cat(
'#################################################################################################
"US Airport.R" has imported a a network of flights between US airports from the igraphdata
package.

This is a large, weighted, directed network. Nodes are airports and edges are flights. Edges are
weighted by total number of passangers. For more information use "?USairports".

The import script has created four objects that represent the network:
     -network_edgelist      (a dataframe of an edgelist and edge attributes)
     -network_nodes         (a dataframe of node attributes)
     -network_igraph        (an igraph object)
     -network_statnet       (a network object compatable with statnet packages like sna & ergm)


Each object name starts, quite generically, with "network_" and ends with the type of object it 
is. Note that the names are generic so that they are  compatable with other scripts you will use
in this course. Feel free to rename the objects for your purposes. 
################################################################################################')

save(network_edgelist, network_igraph, network_nodes, network_statnet, file="USAirports.rda")
```  
#Describing Network Attrributes

The network has 755 nodes and 8228 edges.

```{r}
ls()
vcount(network_igraph)
ecount(network_igraph)
print(network_statnet)
print(network_igraph)
```

# Description of several critical network features

The network is not bipartite. It is a directed and unweighted network.

```{r}
is_bipartite(network_igraph)
is_directed(network_igraph)
is_weighted(network_igraph)
print(network_statnet)
```

# List network attributes: igraph

```{r}
igraph::vertex_attr_names(network_igraph)
igraph::edge_attr_names(network_igraph)
network::list.vertex.attributes(network_statnet)
network::list.edge.attributes(network_statnet)
```

#Summarize network attributes

```{r}
summary(E(network_igraph)$ "Aircraft")
summary(network_statnet %e% "Passengers")
```

#Dyad Census

There are 10449 (mututal), 2574 (asymmetic) and 271612 (null) dyads in the network.

```{r}
igraph::dyad.census(network_igraph)
sna::dyad.census(network_statnet)
```

#Triad Census

```{r}
igraph::triad_census(network_igraph)
sna::triad.census(network_statnet, mode="graph")
```

#Transitivity or Global Clustering

The transitivity of the network data is around .33.

```{r}
transitivity (network_igraph)
gtrans(network_statnet)
```

#Local Transitivity and Clustering

The local clustering (local transitivity) coefficient is .64. 
Interestingly, the global clustering coefficient (.33) is smaller than the local clustering coefficient.

```{r}
transitivity(network_igraph, type="average")
```

#Average path length

The average path length of the network is 3.45.

```{r}
average.path.length(network_igraph, directed=F)
```

#Component Structure

There are 6 components in this network data. One component has 745 member in it, meaning that most of the airports have flights between them. The rest of components has a few members in it ranging from 1 to 3. It suggests that those airports in smaller size components are probably not for commercial airlines, but for other purposes such as airforce base etc.

There seems to be 166 isolates in the data.

There is one isolate airport that we could identity: DET (Coleman A. Young International Airport).

```{r}
names(igraph::components(network_igraph))
igraph::components(network_igraph)$no
igraph::components(network_igraph)$csize # 2 members or 3 members in the network 
isolates(network_statnet) # why are there isolates?
as.vector(network_statnet%v%'vertex.names')[c(isolates(network_statnet))]
```
